Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2016-01-05 document/ms.tex
figs

\section{Single transit search}

Previous automated searches for transits in the \kepler\ light
curves have restricted their results to candidates with at least three
observable transits in the dataset.
This restriction minimizes contamination by false alarms at low
signal-to-noise.
Noise in the light curves introduced by stellar or instrumental variability
can easily masquerade as a small planet with a long orbital period and lead to

\section{Data preparation}\sectlabel{data}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/model_comp.pdf}
\end{center}
\caption{%
Model comparison.
\figlabel{model-comp}}
\end{figure}

>>>>

\section{Data selection \& preparation}\sectlabel{data}

For the purposes of this \paper, we select the 40,000 brightest G and K dwarfs
from the \kepler\ catalog using the following parameters:

        % m = (4200 <= stlr.teff) & (stlr.teff <= 6100)
        % m &= stlr.radius <= 1.15
        % m &= stlr.dataspan > 365.25*2.
        % m &= stlr.dutycycle > 0.6
        % m &= stlr.rrmscdpp07p5 <= 1000.
        % m &= stlr.kepmag < 15.

\begin{itemize}
{\item $4200\unit{K} \le T_\mathfm{eff} \le 6100\unit{K}$}

\end{itemize}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/model_comp.pdf}
\end{center}
\caption{%
Representative examples of candidate events flagged by the initial search.
Each example falls into a different model category and the figure shows the
data as black points and the best fit mean model prediction.
The examples represent the following model categories:
\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
transit.
\figlabel{model-comp}}
\end{figure}
